---
title: "Sensitivity_Analysis"
author: "Anna Calle"
date: "3/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load required libraries
library(tidyverse)
```

Path to sensitivity analysis folder
```{r}
# Create a Root to Extract Files 
if(Sys.info()["sysname"] == "Windows"){ #If operating system is "Windows" use G: Drive
  team_path <- "G:/"
} else { # If it is not (i.e. Mac), use the Google Drive File Stream
  team_path <- "/Volumes/GoogleDrive/"
}

#Create the Full File Path
path <- paste0(team_path, "Shared drives/Bren GP 2020 maricultura/Data/Raw_Data/Active_Data_Layers/Sensitivity_Analysis")

```

Fish Price Sensitivity with farm number constant at 1 farm
```{r}
# Read in raster files using different prices
# Note: price_8 refers to a fish price of $8.6
price_7 <- raster(paste0(path,"/econ_p_7.tif"))
price_8 <- raster(paste0(path,"/econ_p_8.tif"))
price_10 <- raster(paste0(path,"/econ_p_10.tif"))
price_12 <- raster(paste0(path,"/econ_p_12.tif"))
```

Create summaries for each raster to obtain min and max
```{r}
summary_7 <- summary(price_7)
summary_7

summary_8 <- summary(price_8)
summary_8

summary_10 <- summary(price_10)
summary_10

summary_12 <- summary(price_12)
summary_12
```

Means of each raster
```{r}
mean_7 <- cellStats(price_7, 'mean')
mean_8 <- cellStats(price_8, 'mean')
mean_10 <- cellStats(price_10, 'mean')
mean_12 <- cellStats(price_12, 'mean')
```

Farm Sensitivity with fish price constant at $8.6
```{r}
# Read in raster files using different prices
# Note: price_8 refers to a fish price of $8.6
farm_1 <- raster(paste0(path,"/econ_f_1.tif"))
farm_12 <- raster(paste0(path,"/econ_f_12.tif"))
farm_60 <- raster(paste0(path,"/econ_f_60.tif"))
farm_120 <- raster(paste0(path,"/econ_f_120.tif"))
```

Create summaries for each raster to obtain min and max
```{r}
summary_f_1 <- summary(farm_1)
summary_f_1

summary_f_12 <- summary(farm_12)
summary_f_12

summary_f_60 <- summary(farm_60)
summary_f_60

summary_f_120 <- summary(farm_120)
summary_f_120
```

Means of each raster
```{r}
mean_f_1 <- cellStats(farm_1, 'mean')
mean_f_12 <- cellStats(farm_12, 'mean')
mean_f_60 <- cellStats(farm_60, 'mean')
mean_f_120 <- cellStats(farm_120, 'mean')
```

Feed Price Sensitivity with farm number constant at 1 farm, and fish price of $8.5
```{r}
# Read in raster files using different prices
# Note: price_8 refers to a fish price of $8.6
price_feed_252 <- raster(paste0(path,"/econ_feed_252.tif"))
```

Create summaries for each raster to obtain min and max
```{r}
summary_feed_252 <- summary(price_feed_252)
summary_feed_252
```

Means of each raster
```{r}
mean_feed_252 <- cellStats(price_feed_252, 'mean')
```

