---
title: "Suitability"
author: "Anna Calle"
date: "11/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load required packages
library(rnaturalearthdata)
library(rnaturalearth)
library(sf)
library(raster)
library(ggplot2)
library(dplyr)
library(RColorBrewer)
library(ggspatial)
```


Suitability 

- Depth: 25-100m
- Min sea surface temp: >22째C
- Max sea surface temp: <32째C
- Distance to shore: <25 nautical miles
- Current velocity: <1m/s
- Min dissolved oxygen: >4.41 mg/L (70.559 mmol m^3)

Defining variables
```{r}
min_depth <- -25 
max_depth <- -100
min_sst_value <- 22
max_sst_value <- 32
max_dist_shore <- 46300 #25 nautical miles converted to meters
max_cv_value <- 1
min_DO_value <- 70.559

```

Set-Up for Downloading Data Using the "Maricultura" Google Drive File Stream
```{r}
# Create a Root to Extract Files 
if(Sys.info()["sysname"] == "Windows"){ #If operating system is "Windows" use G: Drive
  team_path <- "G:/"
} else { # If it is not (i.e. Mac), use the Google Drive File Stream
  team_path <- "/Volumes/GoogleDrive/"
}

#Create the Full File Path
path <- paste0(team_path, "Shared drives/Bren GP 2020 maricultura/Data/Raw_Data/Active_Data_Layers")

```

CRS
```{r}
# Assign projection: SIRGAS 2000 / Brazil Polyconic
crs_BRA <- "+proj=poly +lat_0=0 +lon_0=-54 +x_0=5000000 +y_0=10000000 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"
```

Source the area function 
```{r}
source("Area_Function.R")
```

EEZ Raster
```{r}
# Read in 1's raster
raster_all_1 <- raster(paste0(path,"/raster_ones.tif"))

# Crop to EEZ
eez_all_1 <- crop(raster_all_1, eez_BRA)

# Save raster (to use in app)
writeRaster(eez_all_1, paste0(path, "/eez_all_1.tif"), overwrite = T)

# Make df
eez_all_1_df <- as.data.frame(eez_all_1, xy = T)

```


Reclassifying depth to have 1s only if it's in between 25-100m, and 0s otherwise
```{r}
# Read in file
depth_mask <- raster(paste0(path,"/depth_mask.tif"))

# Reclassification matrix for depth layer that makes NA background zeros, suitable cells 2, an unsuitable 1
rcl_mat_depth <- c(-Inf, max_depth, 1,
                   max_depth, min_depth, 2,
                   min_depth, 0, 1,
                   0, Inf, 0)

# Reclassify the depth layer
depth_binary_1 <- reclassify(depth_mask,rcl= rcl_mat_depth)

# Adding missing portion of EEZ using an raster cropped to the correct shape of the EEZ

# Overlay with 1's raster with the correct shape of the EEZ
depth_binary_2 <- overlay(depth_binary_1, eez_all_1, fun = function(a, b) {a + b})

# Reclassification matrix for depth layer
rcl_mat_depth_2 <- c(-Inf, 2.1, 0,
                   2.9, 3.1, 1)

# Reclassify the depth layer
depth_binary <- reclassify(depth_binary_2,rcl= rcl_mat_depth_2)

plot(depth_binary)

# Make df
depth_binary_df <- as.data.frame(depth_binary, xy = T)

```

Reclassify min SST layer to have 1s only if it is above 22째C, and 0s otherwise
```{r}
# Read in file
min_sst_mask <- raster(paste0(path,"/min_sst_mask.tif"))

# Reclassification matrix for min SST
rcl_matrix_min <- c( -Inf, min_sst_value, 0,
                min_sst_value, Inf, 1)

# Reclassify min SST
sst_binary_min <- reclassify(min_sst_mask, rcl = rcl_matrix_min)

# Plot reclassified layer
plot(sst_binary_min)
```

Reclassify max SST layer to have 1s only if it is less than 30째C, and 0s otherwise
```{r}
# Read in file
max_sst_mask <- raster(paste0(path,"/max_sst_mask.tif"))

# Reclassify matrix for max SST layer
rcl_matrix_max <- c( -Inf, max_sst_value, 1,
                max_sst_value, Inf, 0)

# Reclassify max SST layer
sst_binary_max <- reclassify(max_sst_mask, rcl = rcl_matrix_max)

# Plot reclassified layer
plot(sst_binary_max)

# Make df
sst_binary_max_df <- as.data.frame(sst_binary_max, xy = T)
```

Reclassify max current velocity to have 1s only if it is less than 1m/s, and 0s otherwise
```{r}
# Read in file
max_cv_mask <- raster(paste0(path,"/max_cv_mask.tif"))

# Reclassification matrix for current layer
rcl_mat_current <- c(-Inf, max_cv_value, 1,
                   max_cv_value, Inf, 0)

# Reclassify the depth layer
current_binary <- reclassify(max_cv_mask ,rcl= rcl_mat_current)

# Plot reclassified layer
plot(current_binary)

# Make df
current_binary_df <- as.data.frame(current_binary, xy = T)

```

Reclassify distance to shore layer to have 1s only if it is less than 25nm, and 0s otherwise
```{r}
# Read in file
dist_shore <- raster(paste0(path,"/dist_shore.tif"))

# Reclassify matrix for distance to shore layer
rcl_matrix_dist_shore <- c( -Inf, 0, 0,
                            0, max_dist_shore, 1,
                            max_dist_shore, Inf, 0)

# Reclassify distance to shore layer
dist_shore_binary <- reclassify(dist_shore, rcl = rcl_matrix_dist_shore)

# Plot reclassified layer
plot(dist_shore_binary)
```

Reclassify DO layer to have 1s only if it is above 200.5 umol, and 0s otherwise
```{r}

# Units? \xbemol/m\x9f mol/ m3
# Read in file
DO_min_mask <- raster(paste0(path,"/DO_min_mask.tif"))

plot(DO_min_mask)

# Reclassification matrix for DO
rcl_matrix_DO <- c( -Inf, min_DO_value, 0,
                min_DO_value, Inf, 1)

# Reclassify DO min
DO_min_binary <- reclassify(DO_min_mask, rcl = rcl_matrix_DO)

# Plot reclassified layer
plot(DO_min_binary)

```

```{r}
##### Sig. wave height? #####
```

Overlay of all layers minus species specific layers for cobia (temperature and DO)
```{r}
# Overlay
all_layers_no_cobia <- overlay(
                       depth_binary,
                       current_binary,
                       dist_shore_binary,
                       mpas_binary,
                       reefs_binary,
                       reefs_artificial_binary,
                       og_pipeline_binary,
                       og_production_binary,
                       shipping_binary,
                       fun = function(a, b, c, d, e, f, g, h, i){a*b*c*d*e*f*g*h*i})

# Plot
plot(all_layers_no_cobia)

# Convert env. constrains raster to dataframe
all_layers_no_cobia_df <- as.data.frame(all_layers_no_cobia, xy = T) %>% 
  mutate(suitable= case_when(
    layer == 1 ~ "Suitable",
    layer != 1 ~ "Not Suitable"
  ))

# Area calculation
suitable_area(all_layers_no_cobia) # 9380.224 km2

```


Overlay of all Layers
```{r}
# Overlay
all_layers <-  overlay(sst_binary_min,
                       sst_binary_max,
                       depth_binary,
                       current_binary,
                       dist_shore_binary,
                       DO_min_binary,
                       mpas_binary,
                       reefs_binary,
                       reefs_artificial_binary,
                       og_pipeline_binary,
                       og_production_binary,
                       shipping_binary,
                       fun = function(a, b, c, d, e, f, g, h, i, j, k, l){a*b*c*d*e*f*g*h*i*j*k*l})

# Plot
plot(all_layers)

# Save raster
writeRaster(all_layers, paste0(path, "/all_layers.tif"), overwrite = T)

# Area calculation
suitable_area(all_layers) # 9380.224 km

round(freq(all_layers, value = 1)*123.424, digits = 0) # resolution is 92.8 * 13.3

```


######################################################
### Code used for presentations or additional graphs

Data for graphs
```{r}
# Read in Brazil's EEZ
eez_BRA <- read_sf(dsn = path,
                layer = "eez_BRA")

# Regions in Brazil
regions_BRA <- read_sf(dsn = path,
                layer = "regions_BRA")

# States in Brazil
states_BRA <- read_sf(dsn = path,
                layer ="states_BRA")

# Coastal cities in Brazil
cities <- read_sf(dsn = path,
                layer ="coastal_cities")

# Brazil's outline in correct projection and cropped to the EEZ's extent
bound_BRA <- ne_countries(scale = 50, country = "Brazil", returnclass = "sf") %>%
  st_transform(crs_BRA) %>% 
  sf::st_crop( bound_BRA, y = extent(eez_BRA))
```



EEZ
```{r}
# Graph with Brazil's outline
eez_all_1_graph <- ggplot() +
    geom_raster(data = eez_all_1_df,
                mapping = aes(x = x, y = y, fill = as.factor(raster_ones))) +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", "Suitable", ""),
    values = c("#EFEFEF", "#0077e6")) +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white"))
  
eez_all_1_graph
```

Depth
```{r}
# Graph with Brazil's outline
depth_binary_graph <-  ggplot() +
    geom_raster(data = depth_binary_df,
                mapping = aes(x = x, y = y, fill = as.factor(layer))) +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", "Suitable", ""),
    values = c("#EFEFEF", "#0077e6")) +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white"))

depth_binary_graph

# Read in file (for presentation)
depth_mask_incomplete <- raster(paste0(path,"/depth_mask_incomplete.tif"))

# Make df for depth mask (for presentation)
depth_mask_df <- as.data.frame(depth_mask_incomplete, xy = T)

# Graph min SST (for presentation)
depth_mask_graph <- ggplot() +
    geom_raster(data = depth_mask_df,
                mapping = aes(x = x, y = y, fill = depth_mask_incomplete)) +
   scale_fill_distiller(palette = "GnBu",
                        guide = FALSE,
                        na.value="white",
                        direction = -1) +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
   theme_void() +
  theme(panel.grid.major = element_line(color = "white"))

depth_mask_graph

# Depth suitable area (for presentation)
suitable_area(depth_binary)
```

Min SST
```{r}
# Make df for min_sst_mask (for presentation)
min_sst_mask_df <- as.data.frame(min_sst_mask, xy = T)

# Graph min SST (for presentation)
min_sst_mask_graph <- ggplot() +
    geom_raster(data = min_sst_mask_df,
                mapping = aes(x = x, y = y, fill = min_sst_mask)) +
   scale_fill_distiller(palette = "Spectral",
                        guide = FALSE,
                        na.value="white") +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
   theme_void() +
  theme(panel.grid.major = element_line(color = "white"))

min_sst_mask_graph

# Area (for presentation)
suitable_area(sst_binary_min)

# Make df
sst_binary_min_df <- as.data.frame(sst_binary_min, xy = T)

# Graph with Brazil's outline
sst_binary_min_graph <- ggplot() +
    geom_raster(data = sst_binary_min_df,
                mapping = aes(x = x, y = y, fill = as.factor(min_sst_mask))) +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", "Suitable", ""),
    values = c("#EFEFEF", "#0077e6")) +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white"))

sst_binary_min_graph

```

Max SST
```{r}

# Graph with Brazil's outline
sst_binary_max_graph <- ggplot() +
    geom_raster(data = sst_binary_max_df,
                mapping = aes(x = x, y = y, fill = as.factor(max_sst_mask))) +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", ""),
    values = c("#0077e6")) +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white"))

sst_binary_max_graph

```

DO
```{r}

# Make df
DO_min_binary_df <- as.data.frame(DO_min_binary, xy = T)

# Graph with Brazil's outline
DO_min_binary_graph <- ggplot() +
    geom_raster(data = DO_min_binary_df,
                mapping = aes(x = x, y = y, fill = as.factor(DO_min_mask))) +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", ""),
    values = c("#0077e6")) +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white"))

DO_min_binary_graph
```

Current velocity
```{r}

# Graph with Brazil's outline
current_binary_graph <- ggplot() +
    geom_raster(data = current_binary_df,
                mapping = aes(x = x, y = y, fill = as.factor(max_cv_mask))) +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", ""),
    values = c("#0077e6")) +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white"))

current_binary_graph
```

Distance to shore
```{r}

# Make df
dist_shore_binary_df <- as.data.frame(dist_shore_binary, xy = T)

# Graph with Brazil's outline
dist_shore_binary_graph <- ggplot() +
    geom_raster(data = dist_shore_binary_df,
                mapping = aes(x = x, y = y, fill = as.factor(dist_shore))) +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", "Suitable", ""),
    values = c("#EFEFEF", "#0077e6")) +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white"))

dist_shore_binary_graph

```

Overlay (without biological)
```{r}
# Create finalized graph
all_layers_no_cobia_graph <- ggplot() +
    geom_raster(data = all_layers_no_cobia_df,
                mapping = aes(x = x, y = y, fill = suitable)) +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", "Suitable", ""),
    values = c("#EFEFEF", "#0077e6")) +
    geom_sf(data = bound_BRA,
            fill = "#DCDBE0") +
  geom_sf(data = regions_BRA,
          size = 0.35,
          color = "#787B7F" ) +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white"))

all_layers_no_cobia_graph
```

Overlay all
```{r}
# Convert raster to dataframe
all_layers_df <- as.data.frame(all_layers, xy = T) %>% 
  mutate(suitable= case_when(
    layer == 1 ~ "Suitable",
    layer != 1 ~ "Not Suitable"
  ))

# Create finalized graph
all_layers_graph <- ggplot() +
    geom_raster(data = all_layers_df,
                mapping = aes(x = x, y = y, fill = suitable)) +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", "Suitable", ""),
    values = c("#EFEFEF", "#0077e6")) +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  geom_sf(data = regions_BRA,
          size = 0.35,
          color = "#787B7F" ) +
  geom_text(data = regions_coords,
            aes(X, Y, label = Name),
            colour = "#787B7F",
            size = 2.5) +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white")) +
   annotation_scale(location = "br", style = "ticks")

all_layers_graph
```

```{r}
# Area all eez = 3827378
# Proportion suitable 9380.224 * 100/3827378 = 0.2450822
# Proportion eliminated = 99.755
```

Zoomed in area
```{r}
# Extent of zoomed in area
# extent_zoomed <- extent(c(6647998, 7500683, 8271044, 9114753)) # slides
# extent_zoomed2 <- extent(c(5842278.1292, 7384689.6834, 7896133.34, 9899060.4164)) # report
extent_zoomed3 <- extent(c(6182933.4418, 7170203.0051, 8517513.8710, 9826513.4517))  # report

# Crop suitability map to zoomed area
zoomed_all_layers <- crop(all_layers, extent_zoomed3)
plot(zoomed_all_layers)

# Convert raster to dataframe
zoomed_all_layers_df <- as.data.frame(zoomed_all_layers, xy = T) %>% 
  mutate(suitable= case_when(
    layer == 1 ~ "Suitable",
    layer != 1 ~ "Not Suitable"
  ))

# Cropping boundaries, regions and states of Brazil
BRA_cropped <- st_crop(bound_BRA, extent_zoomed3)
regions_cropped <- st_crop(regions_BRA, extent_zoomed3)
states_cropped <- st_crop(states_BRA, extent_zoomed3)

# Centroids for regions
regions_centroids <- read_sf(dsn = path,
                layer ="regions_centroids") %>% 
  st_transform(crs_BRA)

# Retrieve coordinates
regions_coords <- as.data.frame(sf::st_coordinates(regions_centroids))
regions_coords$Name <- regions_centroids$NAME_1

# Modifying centroids coord to better fit labels
regions_coords$X[1] <- 5350000
regions_coords$X[2] <- 5300000
regions_coords$X[3] <- 5250000
regions_coords$X[5] <- 6548806
regions_coords$Y[5] <- 9200000

# Centroids for labels (state)
states_centroids <- states_cropped %>% 
  st_centroid()

# Retrieve the coordinates
states_coords <- as.data.frame(sf::st_coordinates(states_centroids))
states_coords$Name <- states_cropped$NAME_1

# Coordinaters of cities
cities_coords <- as.data.frame(sf::st_coordinates(cities))
cities_coords$City <- cities$City

# Modifying centroids coord to better fit labels
states_coords$X[9] <- 6830000
states_coords$X[4] <-6265000
states_coords$Y[4] <-9660000
states_coords$Y[1] <-8887000

# Create finalized graph
zoomed_all_layers_graph <- ggplot() +
    geom_raster(data = zoomed_all_layers_df,
                mapping = aes(x = x, y = y, fill = suitable)) +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", "Suitable", ""),
    values = c("#EFEFEF", "#0077e6")) +
    geom_sf(data = BRA_cropped, fill = "#DCDBE0") +
  geom_point(data = cities_coords,
             aes( x = X, y = Y),
             shape = 21,
             colour = "black",
             fill = "#d7191c",
             size = 2.5) +
  geom_text(data = cities_coords,
            aes( x = X, y = Y,label = City),
            vjust = 0,
            hjust = 1.2,
            color = "#606366") +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white")) +
   annotation_scale(location = "br", style = "ticks")

zoomed_all_layers_graph
```

Biomass Graph
```{r}
library(ggrepel)
biomass_raster <- raster(paste0(path,"/growth_map.tif"))
plot(biomass_raster)

# Sum biomass
sum_biomass <- cellStats(biomass_raster, 'sum') # 93,908 MT
average_biomass <- cellStats(biomass_raster, 'mean') # 1,235 MT


biomass_df <- as.data.frame(biomass_raster, xy = TRUE) 

# Biomass (for presentation)
biomass_graph <- ggplot()  +
  geom_sf(data = eez_BRA, fill = "#EFEFEF", color = "transparent") +
    geom_raster(data = biomass_df,
                mapping = aes(x = x, y = y, fill = growth_map)) +
   scale_fill_gradient(
   low = "#ecb3ff", high = "#330080", na.value = "transparent", name = "Fish Biomass \n(MT/cell)") +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  geom_sf(data = regions_BRA,
          size = 0.35,
          color = "#787B7F" ) +
   theme_void() +
  theme(panel.grid.major = element_line(color = "white")) +
  annotation_scale(location = "br", style = "ticks")

biomass_graph


cropped_biomass <- crop(biomass_raster, extent_zoomed3)
cropped_biomass_df <- as.data.frame(cropped_biomass, xy = TRUE)

# Crop polygon EEZ
eez_BRA_cropped <- st_crop(eez_BRA, extent_zoomed3)

# Graph
biomass_graph_zoom <- ggplot()  +
  geom_sf(data = eez_BRA_cropped, fill = "#EFEFEF", color = "transparent") +
    geom_raster(data = cropped_biomass_df,
                mapping = aes(x = x, y = y, fill = growth_map)) +
  scale_fill_gradient(
   low = "#ecb3ff",
   high = "#330080",
   na.value = "transparent",
   name = "Fish Biomass \n(MT/cell)") +
    geom_sf(data = BRA_cropped, fill = "#DCDBE0") +
     theme_void() +
  geom_sf(data = states_cropped,
          color = "#787B7F") +
  geom_text( data = states_coords,
             aes(x = X, y = Y, label = Name),
             size = 2.5,
             color = "#787B7F") +
  #geom_point(data = cities_coords, 
             #aes( x = X, y = Y),
             #shape = 21,
             #colour = "black",
             #fill = "#d7191c",
             #size = 2.5) +
 # geom_text(data = cities_coords,
           # aes( x = X, y = Y,label = City),
           # vjust = 0,
           # hjust = 1.2,
            #color = "#606366") +
  theme(panel.grid.major = element_line(color = "white")) +
  annotation_scale(location = "br", style = "ticks")


biomass_graph_zoom
```

npv

```{r}

npv_raster <- raster(paste0(path,"/profitability_map.tif"))

npv_df <- as.data.frame(npv_raster, xy = TRUE)

# For legend
scale_range  <- max(maxValue(npv_raster), -minValue(npv_raster)) * c(-1,1)


npv_graph <- ggplot() +
  geom_sf(data = eez_BRA, fill = "#EFEFEF", color = "transparent") +
    geom_raster(data = npv_df,
                mapping = aes(x = x, y = y, fill = profitability_map)) +
   scale_fill_gradient2(
   low = "#d7191c",
  mid = "#d6d651",
  high = "#1a9641",
  midpoint = 0,
   na.value = "transparent",
   name = "NPV - 10 yrs\n(Billion $USD/cell)",
  breaks = seq(-3, 9, 3)) +
  geom_sf(data = regions_BRA,
          size = 0.35,
          color = "#787B7F" ) +
    geom_sf(data = BRA_cropped, fill = "#DCDBE0") +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  geom_sf(data = regions_BRA,
          size = 0.35,
          color = "#787B7F" ) +
   theme_void() +
  theme(panel.grid.major = element_line(color = "white")) +
  annotation_scale(location = "br", style = "ticks")

npv_graph



cropped_npv <- crop(npv_raster, extent_zoomed3)

npv_df_zoom <- as.data.frame(cropped_npv, xy = TRUE)



npv_graph_crop <- ggplot() +
  geom_sf(data = eez_BRA_cropped, fill = "#EFEFEF", color = "transparent") +
    geom_raster(data = npv_df_zoom,
                mapping = aes(x = x, y = y, fill = profitability_map)) +
   scale_fill_gradient2(
   low = "#d7191c",
  mid = "#d6d651",
  high = "#1a9641",
  midpoint = 0,
   na.value = "transparent",
   name = "NPV - 10 yrs\n(Billion $USD/cell)",
  breaks = seq(-3, 16, 3)) +
    geom_sf(data = BRA_cropped, fill = "#DCDBE0") +
 # geom_sf(data = states_cropped,
 #         color = "#787B7F") +
 # geom_text( data = states_coords,
 #            aes(x = X, y = Y, label = Name),
 #            size = 2.5,
 #            color = "#787B7F") +
  geom_point(data = cities_coords,
             aes( x = X, y = Y),
             shape = 21,
             colour = "black",
             fill = "#d7191c",
             size = 2.5) +
  geom_text(data = cities_coords,
           aes( x = X, y = Y,label = City),
           vjust = 0,
           hjust = 1.2,
           color = "#606366") +
   theme_void() +
  theme(panel.grid.major = element_line(color = "white")) +
  annotation_scale(location = "br", style = "ticks")

npv_graph_crop
```

